Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-26 Methods-and-Results.Rmd
AOT-S core need results added

\subsubsection{Core Need}

>>>>

\subsubsection{Core Need}
```{r studentOutModelMLAttNull, include=FALSE}
# create empty list to organize models
mdlStudentOut <- 
  list(
    Att = list(),
    Qlt = list()
  )

# Create and save Model
mdlStudentOut$Att$lmerNull <-
  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), 
             data = dtStudentSupp$studentOutgroupInteraction) # use optim if it does not converge
mdlStudentOut$Att$lmeNull <-
  lme(
    AttitudesDutch ~ 1,
    random = ~ 1 | PID,
    data = dtStudentSupp$studentOutgroupInteraction,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
# summary(Null.Out.ML.r) #or with the lme function
summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)

# Save variances
mdlStudentOut$Att$varNull <- 
  VarCorr(mdlStudentOut$Att$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlStudentOut$Att$tauNull <- 
  as.numeric(mdlStudentOut$Att$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlStudentOut$Att$sigmaNull <- 
  as.numeric(mdlStudentOut$Att$varNull[2])
# The ICC estimate (between/between+within) is:
mdlStudentOut$Att$IccNull <-
  (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))
mdlStudentOut$Att$IccPercNull <-
  ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100
```
```{r studentOutModelInterceptAttCore, include=FALSE}
# Create and save Model
mdlStudentOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFullfillment_cwc,
    random = ~ 1 | PID,
    data = dtStudentSupp$studentOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlStudentOut$Att$lmerInterceptCore <-
    lmer(
      AttitudesDutch ~ KeyNeedFullfillment_cwc + (1 | PID),
      data = dtStudentSupp$studentOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

mdlStudentOut$Att$lmerInterceptCoreCI <- 
  confint(mdlStudentOut$Att$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

# Compare new model to previous step
anova(mdlStudentOut$Att$lmeNull, 
      mdlStudentOut$Att$lmeInterceptCore) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlStudentOut$Att$varInterceptCore <-
  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCore)
```
```{r studentOutModelSlopesAttCore, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlStudentOut$Att$lmeSlopesCore <-
  lme(
    AttitudesDutch ~
      KeyNeedFullfillment_cwc,
    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
    control = lmeControl(opt = "optim"),
    data = dtStudentSupp$studentOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlStudentOut$Att$lmerSlopesCore <- lmer(
    AttitudesDutch ~
      KeyNeedFullfillment_cwc +
      (1 + KeyNeedFullfillment_cwc | PID),
    data = dtStudentSupp$studentOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# all variables standardized within PPT
summ(
  mdlStudentOut$Att$lmerSlopesCoreZ <- lmer(
    AttitudesDutch_zwc ~
      KeyNeedFullfillment_zwc +
      (1 + KeyNeedFullfillment_zwc | PID),
    data = dtStudentSupp$studentOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# standardized coefficients
stdCoef.merMod(mdlStudentOut$Att$lmerSlopesCore)

# 95%CIs
mdlStudentOut$Att$lmerSlopesCoreCI <- confint(mdlStudentOut$Att$lmerSlopesCore)

# Attempts at R^2
r2mlm::r2mlm(mdlStudentOut$Att$lmerSlopesCore, bargraph = TRUE)
mitml::multilevelR2(mdlStudentOut$Att$lmerSlopesCore)
performance::r2(mdlStudentOut$Att$lmerSlopesCore)
performance::model_performance(mdlStudentOut$Att$lmerSlopesCore)
performance::compare_performance(mdlStudentOut$Att$lmerNull, 
                                 mdlStudentOut$Att$lmerInterceptCore, 
                                 mdlStudentOut$Att$lmerSlopesCore)

# Compare new model to previous step
anova(mdlStudentOut$Att$lmeNull, 
      mdlStudentOut$Att$lmeInterceptCore, 
      mdlStudentOut$Att$lmeSlopesCore) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlStudentOut$Att$varSlopesCore <- 
  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCore)

# Assumption Checks:
mdlStudentOut$Att$diagSlopesCore <- 
  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCore, type = "diag")
grid.arrange(
  mdlStudentOut$Att$diagSlopesCore[[1]],
  mdlStudentOut$Att$diagSlopesCore[[2]]$`PID`,
  mdlStudentOut$Att$diagSlopesCore[[3]],
  mdlStudentOut$Att$diagSlopesCore[[4]]
)

# Plot prediction model
mdlStudentOut$Att$predSlopesCore <- 
  dtStudentSupp$studentOutWithinBetween %>% 
  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlStudentOut$Att$predPltSlopesCore <-
    ggplot(data = mdlStudentOut$Att$predSlopesCore, 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
  mdlStudentOut$Att$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

```{r studentOutModelMLQltNull, include=FALSE}
# Create and save Model
mdlStudentOut$Qlt$lmerNull <-
  lme4::lmer(quality_overall ~ 1 + (1 | PID), 
             data = dtStudentSupp$studentOutWithinBetween) # use optim if it does not converge
mdlStudentOut$Qlt$lmeNull <-
  mdlStudentOut$Qlt$lmeNull <-lme(
    quality_overall ~ 1,
    random = ~ 1 | PID,
    data = dtStudentSupp$studentOutWithinBetween,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
# summary(Null.Out.Qual.ML.r) #or with the lme function
summ(mdlStudentOut$Qlt$lmerNull, digits = 3)

# generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000,
#                  parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-Null-CI.csv")

# Save variances
mdlStudentOut$Qlt$varNull <- 
  VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlStudentOut$Qlt$tauNull <- 
  as.numeric(mdlStudentOut$Qlt$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlStudentOut$Qlt$sigmaNull <- 
  as.numeric(mdlStudentOut$Qlt$varNull[2])
# The ICC estimate (between/between+within) is:
mdlStudentOut$Qlt$IccNull <-
  (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))
mdlStudentOut$Qlt$IccPercNull <-
  ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100
```
```{r studentOutModelInterceptQltCore, include=FALSE}
# Create and save Model
mdlStudentOut$Qlt$lmeInterceptCore <-
  lme(
    quality_overall ~ KeyNeedFullfillment_cwc,
    random = ~ 1 | PID,
    data = dtStudentSupp$studentOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlStudentOut$Qlt$lmerInterceptCore <-
    lmer(
      quality_overall ~ KeyNeedFullfillment_cwc + (1 | PID),
      data = dtStudentSupp$studentOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
  confint(mdlStudentOut$Qlt$lmerInterceptCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

# Compare new model to previous step
anova(mdlStudentOut$Qlt$lmeNull, 
      mdlStudentOut$Qlt$lmeInterceptCore) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlStudentOut$Qlt$varInterceptCore <-
  lme4::VarCorr(mdlStudentOut$Qlt$lmeInterceptCore)
```
```{r studentOutModelSlopesQltCore, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlStudentOut$Qlt$lmeSlopesCore <-
  lme(
    quality_overall ~
      KeyNeedFullfillment_cwc,
    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
    control = lmeControl(opt = "optim"),
    data = dtStudentSupp$studentOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlStudentOut$Qlt$lmerSlopesCore <-
    lmer(
      quality_overall ~
        KeyNeedFullfillment_cwc +
        (1 + KeyNeedFullfillment_cwc | PID),
      data = dtStudentSupp$studentOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
  confint(mdlStudentOut$Qlt$lmerSlopesCore)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
#               method="boot",nsim=1000,
#               parallel = "multicore", ncpus = 4, seed = 42),
#          "output/tables/ML-RandomSlopes-CI.csv")

# Compare new model to previous step
anova(mdlStudentOut$Qlt$lmeNull, 
      mdlStudentOut$Qlt$lmeInterceptCore, 
      mdlStudentOut$Qlt$lmeSlopesCore) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlStudentOut$Qlt$varSlopesCore <- 
  lme4::VarCorr(mdlStudentOut$Qlt$lmeSlopesCore)

# Assumption Checks:
mdlStudentOut$Qlt$diagSlopesCore <-
  sjPlot::plot_model(mdlStudentOut$Qlt$lmerSlopesCore, type = "diag")
grid.arrange(
  mdlStudentOut$Qlt$diagSlopesCore[[1]],
  mdlStudentOut$Qlt$diagSlopesCore[[2]]$`PID`,
  mdlStudentOut$Qlt$diagSlopesCore[[3]],
  mdlStudentOut$Qlt$diagSlopesCore[[4]]
)

# Plot prediction model
mdlStudentOut$Qlt$predSlopesCore <- 
  dtStudentSupp$studentOutWithinBetween %>%
  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlStudentOut$Qlt$lmeSlopesCore,
                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlStudentOut$Qlt$predPltSlopesCore <-
    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% dtStudentSupp$studentOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
  mdlStudentOut$Qlt$predPltSlopesCore,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

```
```{r studentOutModelInterceptAttCoreQlt, include=FALSE}
# Create and save Model
mdlStudentOut$Att$lmeInterceptCoreQlt <-
  lme(
    AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc,
    random = ~ 1 | PID,
    data = dtStudentSupp$studentOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlStudentOut$Att$lmerInterceptCoreQlt <-
    lmer(
      AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc + (1 | PID),
      data = dtStudentSupp$studentOutWithinBetween
    ),
  confint = TRUE,
  digits = 3
)

mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
  confint(mdlStudentOut$Att$lmerInterceptCoreQlt)

# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
#                  method="boot",nsim=1000, parallel = "multicore",
#                  ncpus = 4, seed = 42),
#          "output/tables/ML-Inter-CI.csv")

# Compare new model to previous step
anova(
  mdlStudentOut$Att$lmeNull, 
  mdlStudentOut$Att$lmeInterceptCoreQlt
  ) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlStudentOut$Att$varInterceptCoreQlt <-
  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreQlt)
```
```{r studentOutModelSlopesAttCoreQlt, include=FALSE}
# Create and save Model (optimizer needed to reach convergence)
mdlStudentOut$Att$lmeSlopesCoreQlt <-
  lme(
    AttitudesDutch ~
      KeyNeedFullfillment_cwc + quality_overall_cwc,
    random = ~ 1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID,
    control = lmeControl(opt = "optim"),
    data = dtStudentSupp$studentOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlStudentOut$Att$lmerSlopesCoreQlt <- lmer(
    AttitudesDutch ~
      KeyNeedFullfillment_cwc + quality_overall_cwc +
      (1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID),
    data = dtStudentSupp$studentOutWithinBetween,
    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
  ),
  confint = TRUE,
  digits = 3
)

mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
  confint(mdlStudentOut$Att$lmerSlopesCoreQlt)

# Compare new model to previous step
anova(
  mdlStudentOut$Att$lmeNull,
  mdlStudentOut$Att$lmeInterceptCoreQlt,
  mdlStudentOut$Att$lmeSlopesCoreQlt
) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlStudentOut$Att$varSlopesCoreQlt <- 
  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreQlt)

# Assumption Checks:
mdlStudentOut$Att$diagSlopesCoreQlt <- 
  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreQlt, type = "diag")
grid.arrange(
  mdlStudentOut$Att$diagSlopesCoreQlt[[1]],
  mdlStudentOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
  mdlStudentOut$Att$diagSlopesCoreQlt[[3]],
  mdlStudentOut$Att$diagSlopesCoreQlt[[4]]
)

# Plot prediction model
mdlStudentOut$Att$predSlopesCoreQlt <- 
  dtStudentSupp$studentOutWithinBetween %>% 
  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlStudentOut$Att$predPltSlopesCoreQlt <-
    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreQlt.png",
  mdlStudentOut$Att$predPltSlopesCoreQlt,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly. We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`). However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`). These results are consistent with the results in study one and we thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.

### 2021-10-26 Methods-and-Results.tex
AOT-S core need results added

>>>>

We again sequentially tested whether the fulfillment of the core need
during an interaction was (1) related to more positive outgroup
attitudes, (2) higher perceived interaction quality, and (3) whether the
variance explained by the core need is assumed by the perceived
interaction quality if considered jointly. We find that in the
multilevel models, the fulfillment of core situational needs during
outgroup contacts was associated with more positive outgroup attitudes
(random slopes model; \textit{b} = 0.13, \textit{t}(826) = 4.18,
\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}) and also
predicted higher perceived interaction quality (random slopes model;
\textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
\textit{95\%CI}{[}0.28, 0.53{]}). However, if we consider the influences
of core need fulfillment and interaction quality on outgroup attitudes
jointly, we find that virtually all variance is explained by perceived
interaction quality (random slopes mode; \textit{b} = 0.17,
\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
still explained by core need fulfillment (\textit{b} = 0.03,
\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
0.08{]}). These results are consistent with the results in study one and
we thus find support for our hypotheses and can conclude that in this
data set the fulfillment of core situational needs had a significant
influence on outgroup attitudes and that this effect is likely explained
by its effect through perceived interaction quality.
